Mixture distribution data generation

### 2022-02-15 Ch3_samplesize/mess/Datagen_viz.Rmd
Trying to tackle the mess. Moved things around and renamed.

For our toy model, we assume four social groups ($i=4$), where each group has between 4-7 individuals assigned randomly, with a total of 22 individuals in our simulated population.

@@

Now, let's simulate the individuals

@@

Thinking out loud: Let's make the variation for the individuals normal. So, we multiply the variance for that percentage and then estimate it? The mu stays the same, we do a sample from the standard normal? Or do we follow percentages. Since we have a different number of individuals per group, I'd go with the standard normal approach.

@@

>>>>

For our toy model, we assume four social groups ($i=4$), where each group has between 4-7 individuals assigned randomly.

Initially, we only consider the four groups:

@@

We simulate the data coming from this process and then use different sample sizes and thresholds to estimate the tail. 
I think this means that increasing sample size is fine, but it is actually selecting low thresholds that creates the most variation in the estimates.

```{r}
load("Ch3_samplesize/resamp.RData")
# Keep in mind that the pis for this are different and chosen randomly from the toymodel script. 
# pis <- c( 0.1, 0.2, 0.3, 0.4)

resamp.df %>% 
  mutate(diff = (cdfs.hat-true.cdfs), 
         sampsize = factor(all.sampsizes),
         tailthresh = factor(all.qtests))-> resamp.df

resamp.df %>% 
  #filter(., all.sampsizes == "80") %>%  
  ggplot(., aes(x = sampsize, y = diff, color = tailthresh)) +
  geom_boxplot() +
  labs(x = "Sample size", y = "Estimated/True") +
  #scale_y_log10() +
  theme_minimal()

We want to know how "off" the estimates are from the truth.
```{r}
resamp.df %>% 
  group_by(sampsize, tailthresh) %>% 
  summarise(est.bias = signif(mean(diff), 3))

resamp.df %>% 
  group_by(sampsize, tailthresh) %>% 
  summarise(est.bias = signif(mean(diff), 3)) %>% 
  ggplot(., aes(x = sampsize, color = tailthresh, y = est.bias)) +
  geom_point() +
  scale_y_continuous(labels = scales::percent) +
  theme_minimal()

### Now, let's simulate the individuals

@@

@@

```{r}
# Generate the data
